Optogenetic Maxwell Demon to Exploit Intrinsic Noise and Control Cell Differentiation Despite Time Delays and Extrinsic Variability

### 2023-02-02 paper.tex
Minore change to Section 3.1.

We note however, that the improved steady state performance for systems with larger scales, comes at a cost that they also take longer to reach a steady state distribution. This is illustrated in Fig.\ \ref{XXX} which shows the time needed to adapt to a change in the target point $\mathbf{T} = [XXX,XXX]$ to its mirror point $\mathbf{T}_m = [XXX,XXX]$.  
% XXX - Please add a new figure to show this point.  Start with an initial condition that is the steady state with target T and then flip it to T' = T(::-1).  Then solve for P(t) and calculated J(t) from this.    Finally, make a plot of J(t) versus t for the three cases \alpha = 0.2, 1, 2.
 From the figure, it is clear that the smaller systems XXX.
 % XXX - update this to explain what you see in this new figure.

>>>>

We note however, that the improved steady state performance for systems with larger scales, comes at a cost that they also take longer to reach a steady state distribution. This tradeoff is illustrated in Fig.\ \ref{XXX} which shows the performance score $J(t)$ as the system adapts to a change from the original target point $\mathbf{T} = [XXX,XXX]$ to its mirror point $\mathbf{T}_m = [XXX,XXX]$.  
% XXX - Please add a new figure to show this point.  Start with an initial condition that is the steady state with target T and then flip it to T' = T(::-1).  Then solve for P(t) and calculated J(t) from this.    Finally, make a plot of J(t) versus t for the three cases \alpha = 0.2, 1, 2.
 From the figure, it is clear that the smaller systems XXX.
 % XXX - update this to explain what you see in this new figure.
